Hydra Battles and Cie

### 2021-09-12 doc/JFLA2022/paper.tex
minor corrections

% -------------------------------
%%%% For Alectryon

@@

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Hydras and Cie \\
  Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq}

\author{
Pierre Castéran \inst{1}
\and
    Jérémy Damour %\inst{2}
\and
Karl Palmskog %\inst{3}
\and Clément Pit-Claudel %\inst{4}
\and Théo Zimmermann %\inst{5}
}

\institute{
 LaBRI, Université Bordeaux \\
  \email{pierre.casteran@labri.fr}
\and
   University of Miami,
   Miami, Florida, U.S.A.\\
   \email{geoff@cs.miami.edu}\\
\and
   University of Manchester,
   Manchester, U.K.\\
   \email{andrei@voronkov.com}\\
\and
   Chalmers University of Technology,
   Gothenburg, Sweden
\and
   EasyChair
 }

@@

It is important to notice that, for proving this last result, we decided to host and maintain within \emph{Coq-Community} the formalization of primitive recursive function, part of Russel O'Connor work on G\"{o}del's first incompleteness theorem~\cite{OConnor05}.

>>>>

\usepackage[firstpageonly=false, color={[gray]{0.5}},
   scale=2.0, text=DRAFT]{draftwatermark}
% -------------------------------
%%%% For Alectryon

@@

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Hydras and Cie (Draft) \\
  Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq}

\author{
Pierre Castéran \inst{1}
\and
    Jérémy Damour \inst{2}
\and
Karl Palmskog \inst{2}
\and Clément Pit-Claudel \inst{2}
\and Théo Zimmermann %\inst{5}
}

\institute{
 LaBRI, Université Bordeaux \\
  \email{pierre.casteran@labri.fr}
\and
   Ask for agreement !
 }

@@

It is important to notice that, for proving this last result, we decided to host and maintain within \emph{Coq-Community} the formalization of primitive recursive function, part of Russel O'Connor's work on G\"{o}del's first incompleteness theorem~\cite{OConnor05}.

### 2021-09-12 doc/chapter-powers.tex
minor corrections

\begin{Coqsrc}
Fixpoint power`{M: @EMonoid A  E_op E_one E_eq} 
               (x:A) (n:nat) :=
match n with 
| 0%nat => E_one
| S p =>   x * x ^ p
end
where "x ^ n" := (power x n) : M_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma power_eq1 {A:Type} `{M: @EMonoid A  E_op E_one E_eq} 
               (x:A) :  x ^ 0 = E_one.
Proof. reflexivity. Qed.

Lemma power_eq2 {A:Type} `{M: @EMonoid A  E_op E_one E_eq}
                (x:A) (n:nat) :
                x ^ (S n)  = x * x ^ n.
Proof. reflexivity. Qed.

Lemma power_eq3 {A:Type} `{M: @EMonoid A  E_op E_one E_eq}
                (x:A) : x ^ 1 == x.
Proof. cbn; rewrite Eone_right; reflexivity. Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Open Scope M_scope.

Compute 22%Z ^ 20.
\end{Coqsrc}

\begin{Coqanswer}
= 705429498686404044207947776%Z
\end{Coqanswer}

\begin{Coqsrc}
Import Int31.
Coercion phi_inv : Z >-> int31.

Compute (22%int31 ^ 20).
\end{Coqsrc}

\begin{Coqanswer}
   = 2131755008%int31
     : int31
\end{Coqanswer}

@@

\begin{Coqsrc}
Fixpoint binary_power_mult `{M: @EMonoid A E_op E_one E_eq}
             (x a:A)(p:positive) : A 
  :=
  match p with
    | xH =>    a * x
    | xO q => binary_power_mult  (x * x) a q
    | xI q =>   binary_power_mult (x * x) (a * x) q
  end.

Fixpoint Pos_bpow  `{M: @EMonoid A E_op E_one E_eq} 
         (x:A)(p:positive) :=
 match p with
  | xH => x
  | xO q => Pos_bpow  (x * x) q
  | xI q => binary_power_mult (x * x) x q
end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition N_bpow {A} `{M: @EMonoid A E_op E_one E_eq} x (n:N) := 
  match n with 
  | 0%N => E_one
  | Npos p => Pos_bpow x p
  end.

Infix "^b" := N_bpow (at level 30, right associativity): M_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma N_bpow_ok : 
forall (x:A) (n:N),   x ^b n  == x ^ N.to_nat n.
(* Proof omitted *)
\end{Coqsrc}

>>>>

\inputsnippets{Pow/powerDef}

@@

\inputsnippets{Pow/powerEqns}

@@

\inputsnippets{Demo_power/Demopower}

@@

\pagebreak

\emph{From Module~\href{../theories/html/additions.Pow.html}{additions.Pow}}

\inputsnippets{Pow/binaryPowerMult, Pow/PosBpow}

@@

@@

\inputsnippets{Pow/NBpowOk}
\end{itemize}
